---
title: "Get raw data from the database"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 2

---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(
  warning = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  message = FALSE,
  fig.width = 8,
  # fig.height = 6,
  fig.asp = 0.618,
  dpi = 300,
  out.width = "80%")

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
```


## Do a little setup

Create data directories if they don't exist yet.

```{r}
library(dplyr, warn.conflicts = FALSE)
library(L2TDatabase)

# Work relative to RStudio project
wd <- rprojroot::find_rstudio_root_file()

# Create a directory to store the data
create_directory <- function(path) {
  if (!dir.exists(path)) {
    message("Creating directory: ", path)
    dir.create(path, showWarnings = FALSE)
  }
  invisible(path)
}

create_directory(file.path(wd, "data-raw"))
create_directory(file.path(wd, "data"))
```

Connect to the database.

```{r}
# Try to find the file with L2T database information in user's home 
# folder or in this repository
find_database_config <- function() {
  home_config <- path.expand("~/l2t_db.cnf")
  repo_config <- rprojroot::find_rstudio_root_file("l2t_db.cnf")

  if (file.exists(home_config)) {
    home_config
  } else if (file.exists(repo_config)) {
    repo_config
  } else {
    stop("Cannot find `l2t_db.cnf` file")
  }
}

# Connect to the individual databases
l2t_main <- l2t_connect(find_database_config(), "l2t")
l2t_backend <- l2t_connect(find_database_config(), "backend")
l2t_eyetracking <- l2t_connect(find_database_config(), "eyetracking")
```


## Find the eyetracking blocks

### Determine which eyetracking blocks used which stimulus recordings

JE says that we should only use the experiments that used the re-recorded 
stimuli for TimePoint2. We modified the stimuli at TimePoint2 so that the two
dialect versions had similar durations.

These are the tables in the eyetracking database.

```{r}
src_tbls(l2t_eyetracking)
```

Tables with `q_` at the front are queries which contain helpful information
(like Study and ResearchID) alongside the main data in the table. We use the
`q_TrialAttributesByStudy` table to get information about each eyetracking 
trial. 

```{r}
# Dialects used in each block
q_block_dialects <- l2t_eyetracking %>% 
  tbl("q_BlockAttributesByStudy") %>% 
  filter(
    Task == "RWL", 
    BlockAttribute_Name == "Dialect", 
    Study %in% c("DialectSwitch", "MaternalEd")) %>% 
  select(BlockID, BlockAttribute_Value) %>% 
  rename(Dialect = BlockAttribute_Value)

q_block_ages <- l2t_eyetracking %>% 
  tbl("Blocks") %>% 
  select(BlockID, Block_Age)

# Find the blocks that used TP2 stimuli
q_blocks_to_use <- l2t_eyetracking %>% 
  tbl("q_BlockAttributesByStudy") %>% 
  filter(
    Task == "RWL", 
    BlockAttribute_Name == "StimulusSet", 
    BlockAttribute_Value == "TP2",
    Study %in% c("DialectSwitch", "MaternalEd")) %>% 
  select(-BlockAttribute_Name) %>% 
  rename(StimulusSet = BlockAttribute_Value) %>% 
  left_join(q_block_dialects) %>% 
  left_join(q_block_ages)
```

Count the number of blocks in the dialect-varying studies.

```{r}
q_blocks_to_use %>% 
  count(Study, Dialect, StimulusSet) %>% 
  rename(`Num Blocks` = n, `Stimulus Set` = StimulusSet) %>% 
  ungroup() %>% 
  collect() %>% 
  knitr::kable()
```


## Download block and child demographic information

Download child-level information.

```{r}
df_child_info <- tbl(l2t_backend, "Child") %>% 
  left_join(tbl(l2t_backend, "ChildStudy")) %>% 
  left_join(tbl(l2t_backend, "Study")) %>% 
  filter(Study %in% c("DialectSwitch", "MaternalEd")) %>% 
  rename(ResearchID = ShortResearchID) %>% 
  collect() %>% 
  left_join(collect(tbl(l2t_main, "Maternal_Education"))) %>% 
  select(ChildID, ChildStudyID, Study, ResearchID, 
         Female, AAE, LateTalker, CImplant, 
         Maternal_Education, Maternal_Education_Level) 

# Add some helper columns
df_medu_scheme <- data_frame(
  Maternal_Education_Level = c(NA, 1:7),
  Maternal_Education_Group = c(NA, "Low", "Low", "Low", "Mid", 
                               "Mid", "High", "High")
)

df_child_info <- df_child_info %>% 
  left_join(df_medu_scheme) %>%
  mutate(
    Dialect = ifelse(AAE, "AAE", "MAE"),
    Gender = ifelse(Female, "Girl", "Boy")) 

df_child_info$Maternal_Education_Group <- factor(
  df_child_info$Maternal_Education_Group, 
  levels = c("Low", "Mid", "High")
)

df_evt <- tbl(l2t_main, "EVT") %>% 
  select(Study, ResearchID, EVT_Age:EVT_Standard) %>% 
  collect()

df_ppvt <- tbl(l2t_main, "PPVT") %>% 
  select(Study, ResearchID, PPVT_Age:PPVT_Standard) %>% 
  collect()

df_child_vars <- df_child_info %>% 
  select(Study, ResearchID, ChildStudyID, Female:Gender) %>% 
  distinct() %>% 
  left_join(df_evt) %>% 
  left_join(df_ppvt)
```

Attach research IDs and study names to the non-TP1 blocks.

```{r}
df_rwl_blocks <- q_blocks_to_use %>% 
  rename(BlockDialect = Dialect) %>% 
  collect() %>% 
  left_join(df_child_info)
```

Now we count the number of dialects presented to each child to find out who
received more than one version of the experiment.

```{r}
df_children_who_got_multiple_dialects <- df_rwl_blocks %>% 
  select(ChildID, AAE, BlockDialect) %>% 
  distinct() %>% 
  # Count the dialects presented to each child. Find multiple dialect children
  count(AAE, ChildID) %>% 
  filter(n > 1) %>% 
  ungroup() %>% 
  select(ChildID)

df_blocks_to_keep <- df_rwl_blocks %>% 
  inner_join(df_children_who_got_multiple_dialects)
```

One child apparently got three blocks. Figure out which block to manually
exclude.

```{r}
q_blocks_to_use %>% 
  group_by(ResearchID) %>% 
  tally() %>% 
  collect() %>% 
  filter(n > 2) %>% 
  rename(`Num Blocks` = n)

q_blocks_to_use %>% 
  collect() %>% 
  filter(ResearchID == "436D")

# Skip the latest redundant block
df_blocks_to_keep <- df_blocks_to_keep %>% 
  filter(DateTime != "2014-04-01 09:52:14")

# Update the server-side query to use the restricted subset of blocks
q_blocks_to_use <- q_blocks_to_use %>% 
  filter(BlockID %in% df_blocks_to_keep$BlockID)
```


## Download the gaze data

Download the eyetracking data.

```{r}
# Keep just the trials in the blocks we want
q_rwl_trials <- tbl(l2t_eyetracking, "Trials") %>% 
  semi_join(q_blocks_to_use)

# Download the gazes in those trials
df_raw_rwl_looks <- tbl(l2t_eyetracking, "Looks") %>% 
  inner_join(q_rwl_trials) %>% 
  select(TrialID, Time, GazeByImageAOI) %>% 
  collect(n = Inf) 

df_rwl_looks <- df_raw_rwl_looks %>% 
  inner_join(collect(q_rwl_trials)) %>% 
  inner_join(df_blocks_to_keep) %>% 
  rename(TrialNo = Trial_TrialNo) %>% 
  select(ChildID, ChildStudyID, BlockID, TrialID, 
         Study, ResearchID, ChildDialect = Dialect, 
         Version, Basename, StimulusSet, BlockDialect, 
         Block_Age, TrialNo, Time, GazeByImageAOI)
```

Save our work. The eyetracking data has `nrow(df_rwl_looks)` rows, so we save 
it in a compressed csv file. The readr package automatically compresses and 
uncompresses `csv.gz` files.

```{r}
readr::write_csv(df_child_vars, file.path(wd, "data-raw", "child-info.csv"))
readr::write_csv(df_rwl_looks, file.path(wd, "data-raw", "looks.csv.gz"))
```


