---
title: "Eyetracking data screening"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 4
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(
  cache.path = "assets/cache/02-",
  fig.path = "assets/figure/02-",
  warning = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  message = FALSE,
  fig.width = 8,
  fig.asp = 0.618,
  dpi = 300,
  out.width = "80%")

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
options(width = 100)
```

## Setup

Load the looks.

```{r}
library(dplyr, warn.conflicts = FALSE)
library(littlelisteners)

wd <- rprojroot::find_rstudio_root_file()
looks <- readr::read_csv(file.path(wd, "data-raw", "looks.csv.gz"))
```

Data screening settings.

```{r}
screening <- list(
  # determine amount of missing data between:
  min_time = -20,
  max_time = 2020,
  # remove trials with more than ... proportion of missing data
  max_na = .5,
  # blocks should have at least this many trials
  min_blocks = 12
)
```


Define a response code for the `aggregate_looks()` function.

```{r}
resp_def <- create_response_def(
  primary = "Target",
  others = c("PhonologicalFoil", "SemanticFoil", "Unrelated"),
  elsewhere = "tracked",
  missing = NA
)  
```

## Find unreliable trials

Excessive missing data is defined as having more than 50% missing data between 0
and 2000 ms (relative to target onset). Determine the amount of missing data 
during this window for each trials.

```{r}
trial_quality <- looks %>% 
  filter(screening$min_time <= Time, Time <= screening$max_time) 

range(trial_quality$Time)
      
trial_quality <- trial_quality %>% 
  aggregate_looks(resp_def, Study + ResearchID + ChildDialect + 
                    BlockDialect + TrialID ~ GazeByImageAOI) %>% 
  select(Study:TrialID, PropNA)
```

Count the number of bad trials that need to be excluded.

```{r}
# Using UQ to unquote `screening$max_na` so that the created column is
# *not* named `PropNA > screening$max_na` but instead uses the value of
# `screening$max_na` in the column name.
trial_quality %>% 
  count(PropNA > UQ(screening$max_na)) %>% 
  rename(`Num Trials` = n) %>% 
  knitr::kable()

trial_quality %>% 
  count(ChildDialect, BlockDialect, PropNA > UQ(screening$max_na)) %>%  
  rename(`Num Trials` = n) %>% 
  knitr::kable()
```

Remove the bad trials.

```{r}
bad_trials <- trial_quality %>% 
  filter(PropNA >= screening$max_na)

looks_clean_trials <- anti_join(looks, bad_trials)
```

## Find unreliable blocks

Count the number of trials leftover in each block.

```{r}
# Narrow down to one row per trial
trial_counts <- looks_clean_trials %>% 
  select(ChildID:ResearchID, BlockDialect, ChildDialect) %>% 
  distinct() %>% 
  # Count rows in each group
  count(ChildID, ChildStudyID, BlockID, 
        ResearchID, ChildDialect, BlockDialect) %>% 
  arrange(n) %>% 
  rename(`Num Trials in Block` = n)
```

We need to remove these children. They have too few trials in one of the blocks,
so all their data should be removed.

```{r}
children_to_drop <- trial_counts %>% 
  filter(`Num Trials in Block` < screening$min_blocks) 

children_to_drop %>% 
  knitr::kable()
```

Remove the children.

```{r}
looks_clean_blocks <- looks_clean_trials %>% 
  anti_join(children_to_drop %>% select(ChildID) ) 
```

## Data screening counts

Count the number of children and trials at each stage in data screening.

```{r}
cleaning_progression <- list(
  `a. raw data` = looks,
  `b. drop bad trials` = looks_clean_trials, 
  `c. drop children w sparse blocks` = looks_clean_blocks) %>% 
  bind_rows(.id = "Stage")

cleaning_progression %>% 
  group_by(Stage) %>% 
  summarise(
    `Num Children` = n_distinct(ChildID),
    `Num Blocks` = n_distinct(BlockID),
    `Num Trials` = n_distinct(TrialID)) %>% 
  knitr::kable()

cleaning_progression %>% 
  group_by(
    Stage, `Native Dialect` = ChildDialect) %>% 
  summarise(
    `Num Children` = n_distinct(ChildID),
    `Num Blocks` = n_distinct(BlockID),
    `Num Trials` = n_distinct(TrialID)) %>% 
  knitr::kable()

cleaning_progression %>% 
  group_by(
    Stage,
    `Native Dialect` = ChildDialect,
    `Block Dialect` = BlockDialect) %>% 
  summarise(
    `Num Children` = n_distinct(ChildID),
    `Num Blocks` = n_distinct(BlockID),
    `Num Trials` = n_distinct(TrialID)) %>% 
  knitr::kable()
```

### Missing data stats

Data quality stats for remaining children.

```{r}
looks_clean_blocks %>%
  filter(between(Time, -20, 2020)) %>% 
  aggregate_looks(resp_def, ChildDialect + BlockDialect + 
                    ResearchID + TrialID ~ GazeByImageAOI) %>% 
  group_by(ChildDialect, BlockDialect, ResearchID) %>% 
  summarise(
    nGoodTrials = n(),
    Mean_Prop_NA = mean(PropNA)) %>% 
  summarise(
    `N Children` = n(), 
    `Total Useable Trials` = sum(nGoodTrials),
    `Mean N of Useable Trials` = mean(nGoodTrials) %>% round(1), 
    `SD Trials` = sd(nGoodTrials) %>% round(1),
    `Min Trials` = min(nGoodTrials),
    `Max Trials` = max(nGoodTrials),
    `Mean Prop of Missing Data` = mean(Mean_Prop_NA) %>% round(3), 
    `SD Prop Missing` = sd(Mean_Prop_NA) %>% round(3),
    `Min Prop Missing` = min(Mean_Prop_NA) %>% round(3),
    `Max Prop Missing` = max(Mean_Prop_NA) %>% round(3)) %>% 
  knitr::kable()
```

### Clean up

Double check the eyetracking experiment versions.

```{r}
looks_clean_blocks %>% 
  distinct(StimulusSet, Version)
```

Save clean data.

```{r}
looks_clean_blocks %>% 
  select(Study, ResearchID, Basename, ChildDialect, BlockDialect, Block_Age, 
         TrialNo, Time, GazeByImageAOI) %>% 
  readr::write_csv(file.path(wd, "data", "screened.csv.gz"))
```

Update participants data to only have children with eyetracking data.

```{r}
readr::read_csv(file.path(wd, "data-raw", "child-info.csv")) %>% 
  semi_join(looks_clean_blocks) %>% 
  readr::write_csv(file.path(wd, "data", "scores.csv"))
```

***

```{r}
sessioninfo::session_info()
```


