---
title: "Model eyetracking data"
author: "Tristan Mahr"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE, results = 'hide'}
library("knitr")
opts_chunk$set(
  warning = FALSE,
  collapse = TRUE, 
  comment = "#>", 
  message = FALSE,
  fig.width = 8,
  fig.asp = 0.618,
  dpi = 300,
  out.width = "80%")

wd <- rprojroot::find_rstudio_root_file()
opts_knit$set(root.dir = wd)
```

## Setup

```{r, results = 'hide'}
library(dplyr)
library(lme4)
library(ggplot2)
library(hrbrthemes)

# Work relative to RStudio project
wd <- rprojroot::find_rstudio_root_file()

d_m <- readr::read_csv(file.path(wd, "data", "modeling.csv"))
```

These are plotting settings and helpers.

```{r}
stat_mean_se <- function(...) {
  stat_summary(fun.data = mean_se, ...)
}

stat_mean <- function(...) {
  dots <- list(...)
  dots$fun.y <- mean
  if (is.null(dots$geom)) dots$geom <- "line"
  do.call(stat_summary, dots)
}
  
plot_text <- list(
  x_time = "Time (ms) after target noun onset", 
  y_target = "Proportion of looks to named image",
  y_image = "Proportion of looks to image",
  caption_mean_se = "Mean ± SE"
)

legend_bottom <- theme(
  legend.position = "bottom", 
  legend.text = element_text(size = 10), 
  legend.justification = "left")

legend_top <- theme(
  legend.position = "top", 
  legend.text = element_text(size = 10), 
  legend.justification = "left")

colors <- viridis::scale_color_viridis(end = .7, discrete = TRUE)

hline_chance <- geom_hline(yintercept = .25, size = 1.25, color = "#cccccc")
vline_onset <- geom_vline(xintercept = 0, size = 1.25, color = "#cccccc")
```



## Growth curve models

Based on the [visual exploratory data analysis](./03-eyetracking-data.md), there
is no average effect of hearing a non-native dialect on familiar word
recognition. We need to confirm this observation through growth curve analysis.

First, we set some options for the analysis, namely the start and end time of
the analysis window.

```{r}
opts_gca <- list(
  min_time = 250,
  max_time = 1500
)
```

We model looks from `r opts_gca$min_time` to `r opts_gca$max_time` ms.

```{r windows, echo = FALSE}
# Split data into three dataframes, based on whether looks are before, 
# after, or inside analysis window
data_windows <- d_m %>% 
  mutate(
    window = case_when(
      Time < opts_gca$min_time ~ "before",
      opts_gca$max_time < Time ~ "after",
      TRUE ~ "inside")) %>% 
  split(.$window)

  
ggplot() + 
  aes(x = Time, y = Prop_Target) + 
  hline_chance + 
  vline_onset + 
  stat_mean_se(aes(group = HearsNativeDialect), 
               data = bind_rows(data_windows$before, data_windows$after),
               color = "grey50") + 
  stat_mean_se(aes(color = `Child hears`), data = data_windows$inside) +
  colors +
  ylim(0, 1) +
  theme_ipsum_rc(axis_title_size = 11) + 
  legend_top + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target) 

ggplot() + 
  aes(x = Time, y = Prop_Target, 
      group = interaction(ResearchID, HearsNativeDialect)) + 
  hline_chance + 
  vline_onset + 
  stat_mean(data = d_m, color = "grey50") + 
  stat_mean(aes(color = `Child hears`), data = data_windows$inside) +
  colors +
  theme_ipsum_rc(axis_title_size = 11) + 
  legend_top + 
  labs(x = plot_text$x_time, 
       y = plot_text$y_target)
```


We represent time in our growth curve models as a cubic orthogonal polynomial.
This means that we convert out _Time_ variable into three uncorrelated trend
curves. These are the predictors we use to represent time.

```{r, fig.width=4, out.width="50%"}
# Apply analysis window and Create orthogonal polynomial of time
d_m <- d_m %>% 
  filter(opts_gca$min < Time, Time < opts_gca$max_time) %>% 
  polypoly::poly_add_columns(Time, 3, prefix = "ot", scale_width = 1)
```

```{r polypoly, fig.width=4, out.width="50%", echo = FALSE}
d_m %>% 
  distinct(Time, ot1, ot2, ot3) %>% 
  tidyr::gather(Degree, value, -Time) %>% 
  ggplot() + 
    aes(x = Time, y = value, color = Degree) + 
    geom_line() + 
    labs(title = "Trial-time features")
```


We are going to use a _generalized linear mixed effects model_ to perform the
growth curve analysis. 

** write more about this **

```{r, eval = FALSE}
glmer_controls <- glmerControl(
  optimizer = "bobyqa",
  optCtrl = list(maxfun = 2e5))

m <- glmer(
  cbind(Primary, Others) ~ 
    (ot1 + ot2 + ot3) * HearsNativeDialect + 
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m,
  control = glmer_controls,
  family = binomial)
summary(m)
```

```{r, cache = TRUE}
glmer_controls <- glmerControl(
  optimizer = "bobyqa",
  optCtrl = list(maxfun = 2e5))

cond_omitted <- glmer(
  cbind(Primary, Others) ~ 
    (ot1 + ot2 + ot3) + 
    (ot1 + ot2 + ot3 | ResearchID),
  data = d_m, 
  control = glmer_controls,
  family = binomial)
summary(cond_omitted)

cond_as_fixed_eff <- glmer(
  cbind(Primary, Others) ~ 
    (ot1 + ot2 + ot3) * HearsNativeDialect + 
    (ot1 + ot2 + ot3 | ResearchID),
  data = d_m,
  control = glmer_controls,
  family = binomial)
summary(cond_as_fixed_eff)

cond_as_random_eff <- m2b <- glmer(
  cbind(Primary, Others) ~ 
    (ot1 + ot2 + ot3) + 
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m,
  control = glmer_controls,
  family = binomial)
summary(cond_as_random_eff)

cond_as_both <- glmer(
  cbind(Primary, Others) ~ 
    (ot1 + ot2 + ot3) * HearsNativeDialect + 
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m,
  control = glmer_controls,
  family = binomial)
summary(cond_as_both)
```

Use a model comparison on the four variants.

```{r}
anova_results <- anova(cond_omitted, cond_as_fixed_eff, 
                       cond_as_random_eff, cond_as_both) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("model") %>% 
  as_data_frame()

anova_results %>% 
  select(-deviance) %>% 
  mutate_at(c("AIC", "BIC", "logLik"), round) %>% 
  mutate_at("Chisq", round, 2) %>% 
  mutate_at("Pr(>Chisq)", round, 4) %>% 
  knitr::kable()
```

This is kind of unusual. All of the model comparison metrics favor the model
that includes Child x Native Dialect random effects but omits the Native Dialect
fixed effects. My interpretation:

1. For each child, we have two growth curves: The data from hearing their 
   native dialect and the data from hearing the non-native dialect. Their data 
   is _nested_ in these two kinds of blocks.
2. This variability is important for the model, so we include it in 
   the random effects.
3. But on average, hearing one's native dialect or not does not influence 
   the growth curve features in a systematic way. So we can ignore using 
   condition as a predictor.
4. When we include that native dialect in the model's random effects, we are 
   incorporating information about the nesting of the data. Instead of 
   capturing Child x Native Dialect effects, it seems like the random effects 
   are capturing Child x Block of Testing variability.


*** 

next steps:
* compare child dialect vs vocab vs maternal education

```{r, include=FALSE}
d_m %>% 
  mutate(fitted = predict(cond_as_random_eff, 
                          re.form = ~ ot1 + ot2 + ot3 | ResearchID),
         fixef = predict(cond_as_random_eff, re.form = ~ 0)) %>% 
  ggplot() + 
  aes(x = Time, y = fitted - fixef, color = HearsNativeDialect) + 
  stat_mean(aes(group = interaction(ResearchID, HearsNativeDialect)))
```


```{r, eval = FALSE}
d_m_narrow <- d_m %>% 
  filter(!is.na(EVT_Standard), !is.na(Maternal_Education_Group))

m4 <- glmer(
  cbind(Primary, Others) ~ 
    (1 + ot1) * scale(EVT_Standard) + ot2 + ot3 +
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m_narrow,
  control = glmer_controls,
  family = binomial)
summary(m4)

m5 <- glmer(
  cbind(Primary, Others) ~ 
    (1 + ot1) * Dialect + ot2 + ot3 +
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m_narrow,
  control = glmer_controls,
  family = binomial)
summary(m5)

m6 <- glmer(
  cbind(Primary, Others) ~ 
    (1 + ot1) * Dialect + (1 + ot1) * scale(EVT_Standard) + ot2 + ot3 +
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m_narrow,
  control = glmer_controls,
  family = binomial)
summary(m6)

m7 <- glmer(
  cbind(Primary, Others) ~ 
    (1 + ot1) * Maternal_Education_Group + ot2 + ot3 +
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m_narrow,
  control = glmer_controls,
  family = binomial)
summary(m7)

m8 <- glmer(
  cbind(Primary, Others) ~ 
    (1 + ot1) * Maternal_Education_Group + 
     (1 + ot1) * Dialect + 
    ot2 + ot3 +
    (ot1 + ot2 + ot3 | ResearchID / HearsNativeDialect),
  data = d_m_narrow,
  control = glmer_controls,
  family = binomial)
summary(m8)

anova(m4, m5)
anova(m4, m5, m6) 
anova(m4, m5, m6, m7, m8) 
anova(m5, m7, m8) 


anova(m, m2, m2b, m3)
anova(m, m2b, m3)
anova(m, m2b)
anova(m, m2b, m2)
anova(m, m2b, m2, m4b)
```


